---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linProt

<!-- badges: start -->
<!-- badges: end -->

linProtFunc provides a pipeline that allows for that seamless training and
evaluation of linear models for protein function prediction from user
provided labelled AA sequences, including support for regression  tasks.
This package provides visualizations of the patterns learned by the linear
models which can be used to generate novel proteins with optimised
functional characteristics.

## Installation

You can install the development version of linProt like so:

``` r
# install.packages("devtools")
devtools::install_github("benz0id/linProt", build_vignettes = TRUE)
library("benz0id/linProt")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(linProt)
data(rhoData)

examples <- rhoData$data
labels <- rhoData$labels

# Shuffle, partition, and encode data set.
shuffled_datasets <- shuffled_partitions(examples, labels, 650,
                                        encode=encode_onehot)

# Train a linear model to perform regression.
model <- linear_train(shuffled_datasets$e1,
                      shuffled_datasets$l1,
                      shuffled_datasets$e2,
                      shuffled_datasets$l2)

# View the expected influence of each residue on the function, (lambda max
# in this case).

residue_effect_heatmap(model, 380, 410)
plot_cost_over_rep(model)

# Make some predictions.
results <- predict(shuffled_datasets$e2, model)
results[1:5]
shuffled_datasets$l2[1:5]
```

