---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linProt

<!-- badges: start -->
<!-- badges: end -->
Developed for BCB410 at the University of Toronto, taught by Anjali Silva.

This package provides a pipeline that allows for that seamless training and
evaluation of linear models for protein function prediction from user
provided labelled AA sequences, including support for regression  tasks.
This package provides visualizations of the patterns learned by the linear
models which can be used to generate novel proteins with optimised
functional characteristics.

## Installation

You can install the development version of linProt like so:

``` r
# install.packages("devtools")
devtools::install_github("benz0id/linProt", build_vignettes = TRUE)
library("benz0id/linProt")
```

## Example

With this package, you can easily generate, evaluate, and use linear models for
protein function/fitness predictionn tasks.

Here, we generate a linear model to peodict the absorption properties of various 
aligned channel rhodopin proteins using the provided dataset.

```{r example}
library(linProt)
data(rhoData)

examples <- rhoData$data
labels <- rhoData$labels

examples[1]
labels[1]

# Shuffle, partition, and encode data set.
shuffled_datasets <- shuffled_partitions(examples, labels, num_p1 = 650,
                                        encode=encode_onehot)

# Train a linear model to perform regression.
model <- linear_train(train_data = shuffled_datasets$e1,
                      train_labels = shuffled_datasets$l1,
                      valid_data = shuffled_datasets$e2,
                      valid_labels = shuffled_datasets$l2)

# View the expected influence of each residue on the function, (lambda max
# in this case).

residue_effect_heatmap(model, 380, 410)
plot_cost_over_rep(model)

# Make some predictions.
results <- predictions(shuffled_datasets$e2, model)
as.integer(results[1:5])
shuffled_datasets$l2[1:5]
```

See the vignettes for a detailed description of the available functions, which
can provide a manner of different visualizations of the model's attributes,
as well as apply it to protein engineering tasks.

## References

Mei, H., Liao, Z. H., Zhou, Y., & Li, S. Z. (2005). A new set of amino acid
descriptors and its application in peptide QSARs. Biopolymers, 80(6),
775–786. https://doi.org/10.1002/bip.20296

Xu, Y., Verma, D., Sheridan, R. P., Liaw, A., Ma, J., Marshall, N. M.,
McIntosh, J., Sherer, E. C., Svetnik, V., & Johnston, J. M. (2020).
Deep Dive into Machine Learning Models for Protein Engineering.
Journal of Chemical Information and Modeling, 60(6), 2773–2790.
https://doi.org/10.1021/acs.jcim.0c00073

Karasuyama, M., Inoue, K., Nakamura, R., Kandori, H., & Takeuchi, I. (2018).
Understanding Colour Tuning Rules and Predicting Absorption Wavelengths of
Microbial Rhodopsins by Data-Driven Machine-Learning Approach. Scientific
Reports, 8(1). https://doi.org/10.1038/s41598-018-33984-w

Bedbrook, C. N., Yang, K. K., Robinson, J. E., Mackey, E. D., Gradinaru, V.,
& Arnold, F. H. (2019). Machine learning-guided channelrhodopsin engineering
enables minimally invasive optogenetics. Nature Methods, 16(11), 1176–1184.
\hrefhttps://doi.org/10.1038/s41592-019-0583-8


